### 2011-01-20 paper/problemDefinition.tex
Wrote most of Problem Definition

>>>>

\edit{Jason writing this now}

The gait learning problem aims to find a \emph{gait} that maximizes
some performance metric.

Mathematically, we define a gait as a function that specifies
commanded motor positions for a robot over time.  Using this
definition, we require one function per motor.  We can write gaits
without feedback --- also called feed forward gaits --- as

\be
x_i = f_i(t)
\ee

\noindent for commanded position $x_i$ for motor $i$.  The
function depends only on time.  Using the same framework, a gait
including measured motor position, force, or other values could be
written as

\be
x_i = f_i(t, z)
\ee

\noindent for some measurement $z$.  Though perhaps obvious, it is
worth noting that feedforward gaits are deterministic (unless they
include random elements), producing the same command pattern each time
they are run.  The output of a gait that includes feedback, on the
other hand, depends on the actual measurements, and noise in these
measurements may result in different $x_i$ values each time they are
run.

For the system evaluated in this paper, we chose to use only
feedforward gaits.  An interesting extension would be to allow gaits
to depend on the measured servo positions, loads, voltage drops, or
other quantities.

The ultimate goal was to design gaits that were as fast as possible,
so to optimize for speed, our performance metric was displacement over
a period of motion lasting approximately 10 seconds.  For details of
exactly how this displacement was measured, see \secref{foo}.
